A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-05-05 paper.tex
Add my ridiculous new affiliation

\institute{NICTA\thanks{NICTA is funded by the Australian Government as represented by the Department of Broadband,
    Communications and the Digital Economy and the Australian Research Council through the ICT
    Centre of Excellence program.} and UNSW \\
    \email{alexander.legg@nicta.com.au}
    \and Samsung Research America\thanks{Work completed at 
    Carnegie Mellon University}}

>>>>

    \institute{Data61, CSIRO (formerly NICTA\thanks{NICTA is funded by the Australian Government as represented by the Department of Broadband,
    Communications and the Digital Economy and the Australian Research Council through the ICT
Centre of Excellence program.}) and UNSW \\
    \email{alexander.legg@nicta.com.au}
    \and Samsung Research America\thanks{Work completed at 
    Carnegie Mellon University}}
